Elephace: Elephant Re-identification Using Deep Learning

### 2022-05-05 Report/PaperForReview.tex
Add discussions

\section{Conclusion}
\label{sec:conclusion}

>>>>

For elephant detection architectures, we used Yolov4 \cite{yolov4}, Faster R-CNN Inception ResNet V2 1024x1024 \cite{fasterrcnn}, and SSD MobileNet v2 320x320 detection networks and observed that Faster R-CNN and SSD generated precise bounding boxes compared to YOLOV4.

Features obtained from deep learning architectures pre-trained on ImageNet are good differentiators of elephants from other classes. We observed that these features served as a good prior for distinguishing elephant categories.

We observed that image augmentation consisting of left-right flip, small random changes to saturation and hue improved the performance of models. For few shot models, image augmentation helped to improve accuracy by 17\%

We showed that few shot learning model uses fewer images per class to train and performs better than classification model using same deep learning architecture as backbone.

In few shot learning, we observed that using as few images as three per elephant class generated good results with top-1 accuracy of 81\% and top-3 accuracy of 92\%. With use of 7 images per elephant class, we achieved top-1 accuracy of about 99\%

We observed that using entropy regularization to fine-tune few shot learning increased accuracy by 35\%.

We observed that siamese model overfits the data. The training of siamese network will require larger dataset to gain higher validation rate.
